---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clasifierrr

<!-- badges: start -->
<!-- badges: end -->

The goal of clasifierrr is to ...

## Installation

``` r
remotes::install_github("jspaezp/clasifierrr")
```

## Workflow

1. Externally create the masking files for the classification
1. Internally create a parameters data frame
1. use `build_train_multi` to create the training dataset
1. use `ranger` to train the classifier
1. use `classify_img` to classify as many images as you want
1. (optional) use `filter_masks` to remove objects that are too small or too big

## Example

```{r}
library(clasifierrr)
library(EBImage)
library(ranger)
## basic example code
## 
## 
params_df <- tibble::tibble(
    file = c(
        system.file(
            "extdata", "tiny_4T1-shNT-1_layer1.png",
            package = "clasifierrr"),
        system.file(
            "extdata", "tiny_4T1-shNT-1_layer2.png",
            package = "clasifierrr")),
    classif = c("spheroid", "bg"),
    related_file = system.file(
        "extdata", "tiny_4T1-shNT-1.png",
        package = "clasifierrr")
)

params_df
```

### Form of the classifier files

It has to be a file of the same size of the related image, where it is all black
except for the desired classifier section.

Several classifications can be used.

I personally use gimp to generate those, just open the image you want to 
classify, draw on a new layer, disable the main layer and export to a png.

```{r}
display(readImageBw(system.file(
            "extdata", "tiny_4T1-shNT-1_layer1.png",
            package = "clasifierrr")), method = "raster")

display(readImageBw(system.file(
            "extdata", "tiny_4T1-shNT-1_layer2.png",
            package = "clasifierrr")), method = "raster")

base_image <- readImageBw(system.file(
            "extdata", "tiny_4T1-shNT-1.png",
            package = "clasifierrr"))
display(base_image, method = "raster")
```


The classifier is based on the concept of features, which is applying several
filters to the image to detect edges and calculate the consistency with the
neighborhood.

you can use as many filters as you want but
THE FILTER WIDTHS HAVE TO BE ODD NUMBERS, also consider that the more filters,
the more memmory you will need.

```{r}
features <- calc_features(base_image, filter_widths = c(3,5))
head(features, 2)
```


Each of the columns can be made to an image

```{r}
for (i in names(features)) {
    reconstructed_image <- Image(features[[i]], dim(base_image))
    display(reconstructed_image, method = "raster")
    title(main = list(i, col = "yellow"))
}
```



```{r}
trainset <- build_train_multi(params_df, filter_widths = c(3,5))
head(trainset)
```


```{r}
classifier <- ranger(
    pixel_class ~ .,
    data = trainset, 
    num.trees = 100, 
    importance = "impurity", 
    min.node.size = 5, 
    max.depth = 200)
classifier

```

If the classifier was trained using `importance = "impurity"`, you can ask it
to give you the relative importance of the variables used.

```{r}
sort(ranger::importance(classifier), decreasing = TRUE)
```

### Using the classifier on an image

Can be used directly on calculated features ...

```{r}
test_img <- readImageBw(system.file(
        "extdata", "tiny_4T1-shNT-1.png",
        package = "clasifierrr"))

test_feat <- calc_features(test_img, filter_widths = c(3,5))

class_img <- classify_img(
    classifier, 
    feature_frame = test_feat, 
    dims = dim(test_img), 
    class_highlight = "spheroid")
display(class_img, method = "raster")
```

It can also be used on a raw image ...

```{r}
class_img <- classify_img(
  classifier, 
  img = test_img, 
  filter_widths = c(3,5))
display(colorLabels(class_img), method = "raster")
```

And as well in a system file

```{r}
class_img <- classify_img(
  classifier,
  path = system.file(
    "extdata", "tiny_4T1-shNT-1.png",
    package = "clasifierrr"),
  filter_widths = c(3,5), 
  class_highlight = "spheroid")

display(class_img, method = "raster")
```

### Cleaning the final image

The final image can be cleaned manually or using `filter_masks`,
which can remove stuff either too big or small.

As a reminder, white regions are considered objects, so if your object is black,
try running something like `img <- 1- img`

```{r}
display(dilate(class_img, makeBrush(3, "disc")), method = "raster")
```

```{r}
display(colorLabels(bwlabel(class_img)), method = "raster")
```


```{r}
filt_class_img <- filter_masks(class_img, min_radius = 30, max_radius = 1000)

display(
    filt_class_img,
    method = "raster")

display(colorLabels(bwlabel(filt_class_img)), method = "raster")

table(filt_class_img)

filt_class_img
```

