---
title: "features"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{features}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(clasifierrr)
library(EBImage)
```

```{r}
base_image <- readImageBw(system.file(
            "extdata", "4T1-shNT-1.png",
            package = "clasifierrr"))
display(base_image, method = "raster")
```

The features are just a series of filters applied to the main image.
So it converts an image of heigh y and length x into a data frame of `x * y`
number of rows and one column per feature.

```{r}
feature_df <- calc_features(base_image, filter_widths = c(3, 15, 31))
head(feature_df)
```

you can see the features that were calculated by using the following function

```{r fig.height=12, fig.width=12}
display_filters(feature_df, dims = dim(base_image))
display_filters(feature_df, dims = dim(base_image), scale = TRUE)
```

In order to show what each of them does, lets use a really simple image

```{r}
shapes <- readImage(system.file('images', 'shapes.png', package = 'EBImage'))
logo <- shapes[110:512,1:130]

logo_feature_df <- calc_features(logo, filter_widths = c(3, 5, 15))
head(logo_feature_df)
display_filters(logo_feature_df, dims = dim(logo), scale = TRUE)

```

Note how some filters totally remove the inner spaces of the letters and
preserve the edges, whilst others do some sort of the opposite.
