---
title: "performance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{performance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(clasifierrr)
library(EBImage)
```

We will start with the same files as the ones in the readme

```{r}
params_df <- tibble::tibble(
    file = c(
        system.file(
            "extdata", "4T1-shNT-1_layer1.png",
            package = "clasifierrr"),
        system.file(
            "extdata", "4T1-shNT-1_layer2.png",
            package = "clasifierrr")),
    classif = c("spheroid", "bg"),
    related_file = system.file(
        "extdata", "4T1-shNT-1.png",
        package = "clasifierrr")
)

params_df
```

```{r}
base_image <- readImageBw(system.file(
            "extdata", "4T1-shNT-1.png",
            package = "clasifierrr"))
display(base_image, method = "raster")
```


```{r}
time_taken_full <- system.time({
    features <- calc_features(
        base_image, 
        filter_widths = c(3,7,15))
})

time_taken_full
object.size(features)
```

we can notice that it takes `r time_taken_full[[3]]` 
seconds to achieve the calculation and the `features`
object ocupies 
`r format(object.size(features), units = "Mb")`.

Nonetheless, since we basically are doing one calculation
per pixels, per filter, decreasing the number of pixels would
decrease the number of calculation by that number. 
And therefore, decreasing the size will accelerate the speed
with the square of that reduction (since its a 2d image)

```{r}
newsize <- as.integer(ncol(base_image)/2)
shrunk_image <- resize(base_image, w = newsize)

time_taken_shrunk <- system.time({
    shrunk_features <- calc_features(
        shrunk_image, 
        filter_widths = c(3,7,15))
})

time_taken_shrunk
object.size(shrunk_features)
```


we can notice that now it takes `r time_taken_shrunk[[3]]` 
seconds to achieve the calculation and the `shrunk_features`
object ocupies 
`r format(object.size(shrunk_features), units = "Mb")`.

which is a `r time_taken_full[[3]]/time_taken_shrunk[[3]]`
fold decrease in time and 
`r object.size(features)/object.size(shrunk_features)`
decrease in used memmory

lets take a look at the actual filters ...


```{r}

image_shrunk_list <- purrr::map(names(features), ~ Image(shrunk_features[[.x]], dim(shrunk_image)))
image_full_list <- purrr::map(names(features), ~ Image(features[[.x]], dim(base_image)))

display(combine(image_shrunk_list), method = "raster", all = TRUE)
display(combine(image_full_list), method = "raster", all = TRUE)
```

Note how, since the filter sizes are still the same,
but the image size is different, the filters have slightly
different effects.

now ... I have implemented a way to make this automatic
for the multiple case set.

For that you need to write a function that does the 
processing you want and pass it as an argument to 
`preprocess_fun_img` and `preprocess_fun_mask`

```{r}
half_image <- function(x) {
    newsize <- as.integer(ncol(x)/2)
    shrunk_image <- resize(x, w = newsize)
    return(shrunk_image)
}
```


```{r}
multi_time_full <- system.time({
    trainset <- build_train_multi(
        params_df, 
        train_size_each = 5000, 
        filter_widths = c(3,7,15))
})

multi_time_shrunk <- system.time({
    trainset <- build_train_multi(
        params_df, 
        preprocess_fun_img = half_image,
        preprocess_fun_mask = half_image, 
        train_size_each = 5000, 
        filter_widths = c(3,7,15))
})

multi_time_full
multi_time_shrunk
head(trainset)
```

In this case it would be a increase in `r multi_time_full[[3]]/multi_time_shrunk[[3]]` 
times of computation.


Preprocessing functions can be much more complicated ...


```{r}
preprocess_img <- function(x) {
    x <- correct_light(x, chunk_width = 11)
    x <- half_image(x)
    x <- x - min(min(x), 0)
    x <- x/max(x)
    return(x)
}

preprocessed_image <- preprocess_img(base_image)
display(base_image, method = "raster")
display(preprocessed_image, method = "raster")
```


```{r}
multi_time_shrunk <- system.time({
    trainset_preproc <- build_train_multi(
        params_df, 
        preprocess_fun_img = preprocess_img,
        preprocess_fun_mask = half_image, 
        train_size_each = 5000, 
        filter_widths = c(3,7,15))
})
```


## Prediction performance

Well ... a semi-good measure of prediction accuracy is the out of bag prediction
error (OOB for short) and it is posible to modulate several parameters that can
impact that.

```{r}
library(ranger)
train_params_grid <- as.data.frame(expand.grid(
    num.trees = c(50, 100, 200), 
    min.node.size = c(1, 5, 20, 50),
    max.depth = c(0, 5, 10, 50, 200)))

# Since we are good scientists we will run it in triplicate ...
train_params_grid <- rbind(train_params_grid,train_params_grid,train_params_grid)

small_trainset <- trainset[sample(1:nrow(trainset), 5000),]

forests <- purrr::pmap(
    train_params_grid, 
    function(num.trees, min.node.size, max.depth) {
        ranger(
            pixel_class ~ .,
            data = small_trainset, 
            num.trees = num.trees, 
            importance = "impurity",
            min.node.size = min.node.size,
            max.depth = max.depth)})

train_params_grid$oob_error <- purrr::map_dbl(forests, ~ .x$prediction.error) 

```

these are just the series of plots I would do to ceck which one works better...

```{r fig.height=3, fig.width=5}
require(ggplot2)

ggplot(train_params_grid,
       aes(y = oob_error, x = num.trees, 
           colour = factor(min.node.size))) +
    geom_point() + 
    facet_wrap(~ max.depth, labeller = label_both) + 
    geom_point(
        data = train_params_grid[,-3],
        alpha = 0.1, colour = "#666666",
        aes(y = oob_error, x = num.trees),
        inherit.aes = FALSE) +
    theme_bw()
```


```{r}
img <- preprocess_img(readImageBw(params_df$related_file[[1]]))
dims_use <- dim(img)
feats <- calc_features(img, filter_widths = c(3,7,15))

my_class_fun <- function(classifier) {
    tt <- system.time({
        class_img <- classify_img(
            feature_frame = feats,
            classifier = classifier, 
            dims = dims_use,
            class_highlight = "_sphere") 
    })
    
    return(list(class_img, tt))
}

suppressMessages({
    class_results <- purrr::map(forests, my_class_fun)
})

```

```{r}
train_params_grid$predict_time <- purrr::map_dbl(class_results, ~.x[[2]][[3]])

ggplot(train_params_grid,
       aes(y = predict_time, x = num.trees, 
           colour = factor(min.node.size),
           group = interaction(min.node.size, num.trees))) +
    geom_boxplot() + 
    facet_wrap(~ max.depth, labeller = label_both) +
    theme_bw()

ggplot(train_params_grid,
       aes(y = predict_time, x = factor(min.node.size), 
           colour = factor(max.depth),
           group = interaction(min.node.size, max.depth))) +
    geom_boxplot() + 
    theme_bw()

```


```{r}

ggplot(train_params_grid,
       aes(y = oob_error, x = predict_time, colour = factor(num.trees))) +
    geom_point() + 
    theme_bw()

ggplot(train_params_grid,
       aes(y = oob_error, x = predict_time, colour = factor(min.node.size))) +
    geom_point() + 
    theme_bw()

ggplot(train_params_grid,
       aes(y = oob_error, x = predict_time, colour = factor(max.depth))) +
    geom_point() + 
    theme_bw()
```

